Paper Summary

### 2024-11-02 Paper_Summary.Rmd
Added new test code. Note: Not fully working yet.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('ggplot2')
#install.packages('lme4')
#install.packages('lmerTest')
#install.packages('MuMIn')
#install.packages('MASS')
#install.packages('dplyr')
#install.packages('tidyr')
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(MASS)
library(dplyr)
library(tidyr)
```

```{r Assay 1: Figure 1a. Simulation & Analysis}
# Trait of Interest:

@@

```{r Assay 1: Figure 1b. Simulation & Analysis}

@@

  # Turn plot outline into a box to make it more cutesy
  box()
```
```{r Assay 2: Figure 2. Simulation & Analysis}
low.vial<-rnorm(35, 1, 0.1)
high.vial<-rnorm(35, 1, 0.1)
low.cage<-rnorm(35, 1, 0.1)
high.cage<-rnorm(35, 1, 0.1)
g<-sample(1:4, 140, replace=TRUE)
error<-ifelse(g==1, 0.1, ifelse(g==2, 0.5, 1.5))
g<-as.factor(g)
response<-24*low.vial+17*high.vial+30*low.cage+28*high.cage+rnorm(140, mean=0, sd=0.1)
data<-cbind.data.frame(response, low.vial, high.vial, low.cage, high.cage)
model1<-glm(response~low.vial+high.vial+low.cage+high.cage, data=data)
summary(model1)
anova(model1)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('ggplot2')
#install.packages('lme4')
#install.packages('lmerTest')
#install.packages('MuMIn')
#install.packages('MASS')
#install.packages('dplyr')
#install.packages('tidyr')
#install.packages('car')
#install.packages('pbkrtest')
#install.packages('pscl')
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(MASS)
library(dplyr)
library(tidyr)
library(car)
library(pbkrtest)
library(pscl)
```

```{r Assay 1: Figure 1a. Data Simulation & Analysis}

```

```{r test}
# Simulate Trait of Interest
rnorm(1000, 10, 1)->trait_of_interest ### change this to be a trait that you're actually interested in, with an appropriate distribution!

plot(density(trait_of_interest))
min(trait_of_interest)
max(trait_of_interest)

yes<-sample(trait_of_interest, 500, replace=FALSE, prob = ifelse(trait_of_interest>0, 0.95, 0.15)) #### play with this line! Is the test statistically significant. When is it not?
predictor_t.test<-(trait_of_interest %in% yes)

cbind.data.frame(trait_of_interest, predictor_t.test)->data

mean(data[which(data$predictor_t.test==TRUE),1])
mean(data[which(data$predictor_t.test==FALSE),1])
t.test(trait_of_interest~predictor_t.test, data=data) ### this does a two sample t-test. What would a one sample t test be testing? How would you do that?

### plots our two samples for distribution
plot(density(data[which(data$predictor_t.test==FALSE),1]), col="red", main="Two sample t test")
lines(density(data[which(data$predictor_t.test==TRUE),1]), ylim=c(0, 0.1), xlim=c(-20,20), main="Two Sample T test")

test1<-sample(trait_of_interest, 200, replace=FALSE, prob = ifelse(trait_of_interest>7, 0.95, 0.15))
test2<-sample(trait_of_interest[which(trait_of_interest %in% test1 == FALSE)], 200, replace=FALSE, prob = ifelse(trait_of_interest[which(trait_of_interest %in% test1 == FALSE)] >4, 0.95, 0.15))
test3<-sample(trait_of_interest[which(trait_of_interest %in% test2 == FALSE | trait_of_interest %in% test1 ==FALSE)], 200, replace=FALSE, prob = ifelse(trait_of_interest[which(trait_of_interest %in% test2 == FALSE | trait_of_interest %in% test1 == FALSE)] >0, 0.95, 0.15))
test4<-sample(trait_of_interest[which(trait_of_interest %in% test2 == FALSE | trait_of_interest %in% test1 ==FALSE | trait_of_interest %in% test3 == FALSE)], 200, replace=FALSE, prob = ifelse(trait_of_interest[which(trait_of_interest %in% test2 == FALSE | trait_of_interest %in% test1 ==FALSE | trait_of_interest %in% test3 == FALSE)] >-4, 0.95, 0.15))
test5<-trait_of_interest[which(trait_of_interest %in% test1 == FALSE| trait_of_interest %in% test2 == FALSE | trait_of_interest %in% test3 == FALSE | trait_of_interest %in% test4 == FALSE)]

plot(density(test1), ylim=c(0, 0.1), main="Anovas")
lines(density(test2), col="red")
lines(density(test3), col="blue")
lines(density(test4), col="purple")
lines(density(test5), col="yellow")

anova_predictor<-data.frame(ifelse(trait_of_interest %in% test1 == TRUE, "group1", ifelse(trait_of_interest %in% test2 == TRUE, "group2", ifelse(trait_of_interest %in% test3 == TRUE, "group3", ifelse(trait_of_interest %in% test4 == TRUE, "group4", "group5")))))

data2<-cbind.data.frame(data, anova_predictor)
names(data2)<-c("trait_of_interest", "predictor_t.test", "anova_predictor")

anova(aov(trait_of_interest~anova_predictor, data=data2)) ### what does this do?

anova(lm(trait_of_interest~anova_predictor, data=data2)) ### what does this do? 
summary(aov(trait_of_interest~anova_predictor, data=data2)) ### what does this do? What do you notice about the last three tests?

```

```{r Assay 1: Figure 1a. Plot}
# Trait of Interest:

@@

```{r Assay 1: Figure 1b. Data Simulation & Analysis}
# RNG time! - Let's keep it consistent 
set.seed(123)

# Number of observations made - 2 females, 3 times a day for 3 days * ten replicates for each arena = 180 observations per environment type.
N = 180

# Changing the effect sizes to get the same values as the paper
effect_arena <- 2.0       # Main effect of Arena
effect_size <- 0.5        # Main effect of Size
effect_interaction <- 2.0  # Interaction effect

# Data simulation time! - Different means for different groups
feeding_count <- c(
  rnorm(N, mean = 6.5, sd = 1), # Large females in vials
  rnorm(N, mean = 13.5 + effect_arena, sd = 1), # Large females in cages
  rnorm(N, mean = 10 + effect_size, sd = 1), # Small females in vials
  rnorm(N, mean = 8.5 + effect_arena + (effect_size * (1 + effect_interaction)), sd = 1) # Small females in cages
)

# Making sure that FeedingCount is a positive float (can't eat negative amounts!)
feeding_count <- ifelse(feeding_count <= 0, feeding_count + 0.1, feeding_count)

# Let's make all of this into a data frame - matrix time :(
data <- data.frame(
  Arena = factor(rep(c('vial', 'cage'), each = N * 2)),
  Size = factor(rep(c('large', 'small'), times = N * 2)),
  FeedingCount = feeding_count
)

model_gaussian <- glm(FeedingCount ~ Arena * Size, data = data, family = gaussian(link = 'log'))

summary(model_gaussian)

# Use lmerTest to get F-statistics and p-values
anova_result <- anova(model_gaussian, test = "F")

# Print the results
print(anova_result)

```

```{r Assay 1: Figure 1b. Plot}

@@

  # Turn plot outline into a box to make it more cutesy
  box()
```

```{r Assay 2: Figure 2. Data Simulation & Analysis}
low.vial<-rnorm(35, 1, 0.1)
high.vial<-rnorm(35, 1, 0.1)
low.cage<-rnorm(35, 1, 0.1)
high.cage<-rnorm(35, 1, 0.1)
g<-sample(1:4, 140, replace=TRUE)
error<-ifelse(g==1, 0.1, ifelse(g==2, 0.5, 1.5))
g<-as.factor(g)
response<-24*low.vial+17*high.vial+30*low.cage+28*high.cage+rnorm(140, mean=0, sd=0.1)
data<-cbind.data.frame(response, low.vial, high.vial, low.cage, high.cage)
model1<-glm(response~low.vial+high.vial+low.cage+high.cage, data=data)
summary(model1)
anova(model1)
```
